### 2015-06-21 Manuscript/Supplementary/Supplementary.tex
Revised methods
Removed supp pdf

\subsection{Google scholars}
To make sure we didn't miss any extra matrix that wasn't available on one of these repository, we ran a Google Scholar search on the 5th of January. We used the following key words:

@@

\section{Supplementary results}
The following section contains supplementary results to the main body: the available data structure using the NTI and the PD metric; the proportion of available data and the data structure for all the matrices (including the matrices with less than 100 characters); and phylogenetical representation of the data availability per order (excluding Cetartiodactyla and Carnivora, present in the main body).

\renewcommand\baselinestretch{1.2}\selectfont
\begin{center}
\input{Supplementary/Supp_data_structureNTI}
\end{center}
\renewcommand\baselinestretch{2}\selectfont

\renewcommand\baselinestretch{1.2}\selectfont
\begin{center}
\input{Supplementary/Supp_data_structurePD}
\end{center}
\renewcommand\baselinestretch{2}\selectfont

\renewcommand\baselinestretch{1.2}\selectfont
\begin{center}
\input{Supplementary/morpho_taxa_proportion_threshold1}
\end{center}
\renewcommand\baselinestretch{2}\selectfont

\renewcommand\baselinestretch{1.2}\selectfont
\begin{center}
\input{Supplementary/Supp_data_structureNRI_threshold1}
\end{center}
\renewcommand\baselinestretch{2}\selectfont

\renewcommand\baselinestretch{1.2}\selectfont
\begin{center}
\input{Supplementary/Supp_data_structureNTI_threshold1}
\end{center}
\renewcommand\baselinestretch{2}\selectfont

\renewcommand\baselinestretch{1.2}\selectfont
\begin{center}
\input{Supplementary/Supp_data_structurePD_threshold1}
\end{center}
\renewcommand\baselinestretch{2}\selectfont

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_AFROSORICIDA.pdf}
\caption{Distribution of available morphological data across Afrosoricida. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Afrosoricida}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_CHIROPTERA.pdf}
\caption{Distribution of available morphological data across Chiroptera. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Chiroptera}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_CINGULATA.pdf}
\caption{Distribution of available morphological data across Cingulata. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Cingulata}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_DASYUROMORPHIA.pdf}
\caption{Distribution of available morphological data across Dasyuromorphia. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Dasyuromorphia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_DIDELPHIMORPHIA.pdf}
\caption{Distribution of available morphological data across Didelphimorphia. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Didelphimorphia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_DIPROTODONTIA.pdf}
\caption{Distribution of available morphological data across Diprotodontia. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Diprotodontia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_ERINACEOMORPHA.pdf}
\caption{Distribution of available morphological data across Erinaceomorpha. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Erinaceomorpha}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_PILOSA.pdf}
\caption{Distribution of available morphological data across Pilosa. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Pilosa}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_PRIMATES.pdf}
\caption{Distribution of available morphological data across Primates. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Primates}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_RODENTIA.pdf}
\caption{Distribution of available morphological data across Rodentia. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Rodentia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_SCANDENTIA.pdf}
\caption{Distribution of available morphological data across Scandentia. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Scandentia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_SORICOMORPHA.pdf}
\caption{Distribution of available morphological data across Soricomorpha. Edges are colored in grey when no morphological data is available or in red when data is available.}
\label{Supp_Figure_Phylo-Soricomorpha}
\end{figure}

>>>>

\subsection{Google scholars}
To make sure we didn't miss any extra matrix that wasn't available on one of these repository, we ran a Google Scholar search on the 5th of January. 
We downloaded the additional cladistic matrices from the 20 first search results matching with our selected keywords and with any of the 35 taxonomic levels (mammals Orders, Infraclasses and Class).
We used the following key words:

@@

\section{Supplementary results}
The following section contains supplementary results to the main body: the available data structure using the NTI and the PD metric; the proportion of available data and the data structure for all the matrices (including the matrices with less than 100 characters); and phylogenetical representation of the data availability per order (excluding Primates and Carnivora, present in the main body).

\input{Results_1c.tex}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_AFROSORICIDA.pdf}
\caption{Distribution of available morphological data across Afrosoricida. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Afrosoricida}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_CHIROPTERA.pdf}
\caption{Distribution of available morphological data across Chiroptera. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Chiroptera}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_CINGULATA.pdf}
\caption{Distribution of available morphological data across Cingulata. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Cingulata}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_DASYUROMORPHIA.pdf}
\caption{Distribution of available morphological data across Dasyuromorphia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Dasyuromorphia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_DIDELPHIMORPHIA.pdf}
\caption{Distribution of available morphological data across Didelphimorphia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Didelphimorphia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_DIPROTODONTIA.pdf}
\caption{Distribution of available morphological data across Diprotodontia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Diprotodontia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_ERINACEOMORPHA.pdf}
\caption{Distribution of available morphological data across Erinaceomorpha. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Erinaceomorpha}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_PILOSA.pdf}
\caption{Distribution of available morphological data across Pilosa. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Pilosa}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_CETARTIODACTYLA.pdf}
\caption{Distribution of available morphological data across Cetartiodactyla. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Primates}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_RODENTIA.pdf}
\caption{Distribution of available morphological data across Rodentia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Rodentia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_SCANDENTIA.pdf}
\caption{Distribution of available morphological data across Scandentia. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Scandentia}
\end{figure}

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{Supplementary/Supp_figure_SORICOMORPHA.pdf}
\caption{Distribution of available morphological data across Soricomorpha. Edges are colored in grey when no morphological data is available or in blue when data is available.}
\label{Supp_Figure_Phylo-Soricomorpha}
\end{figure}
